Hydra battles in Coq

### 2020-10-18 doc/hydras.tex
removing the useless/too-weak oplus_rect

\textbf{Hint:}   Beware of the instances associated with sum and product of notations!
  You may consider additional fields such as ``there is a greatest element'' 
to make the sum and product of notations ``compositional''.

@@

\subsubsection{A hand-made induction principle}
\label{sec:orgheadline85}

\index{Coq!Commands!Functional Scheme}

\emph{Coq} contains a command  \texttt{Functional Scheme} that 
generates induction principles which correspond to recursive functions.
Unfortunately, the current version ( \texttt{8.11.0} ) doesn't work on \texttt{oplus},
probably because of the inner \texttt{Fix}.

\begin{Coqsrc}
Functional Scheme oplus_ind := Induction for oplus Sort Prop.
\end{Coqsrc}

\begin{Coqanswer}
Error: Anomaly "todo." Please report at http://coq.inria.fr/bugs/.
\end{Coqanswer}

Fortunately, it's a good exercise for a semi-experienced user, to write
her/him-self induction principles similar to the ones returned by
\texttt{Functional Scheme}.

\begin{itemize}
\item First, we chose to write a version for sort \texttt{Type}, since versions
for sorts \texttt{Prop} and \texttt{Set} can be easily derived from
the former one. According to \emph{Coq}'s naming politics, we will call our 
principle \texttt{oplus\_rect}

\item The conclusion of \texttt{oplus\_rect} will be (\texttt{$P$ a b (oplus a b)}),
where $P$ is an arbitrary function of type 
\texttt{T1 -> T1 -> T1 -> Type}

\item The premises of \texttt{oplus\_rect} will describe how to build an induction 
on the graph of \texttt{oplus}.
\end{itemize}

We are now ready to state and prove \texttt{oplus\_rect}, and the reader
will note that the statement is longer than the proof script itself,
which is a standard proof by induction, simplification and case-analysis 
that follows  \texttt{oplus}'s definition.

We associate also a tactic to the application of \texttt{oplus\_rect}.

\begin{Coqsrc}
 Lemma oplus_rect:
      forall P: T1 -> T1 -> T1 -> Type, 
        (forall a:T1, P zero a a) ->
        (forall a: T1, P a zero a) ->
        (forall a1 n1 b1 a2 n2 b2 o,
           compare a1 a2 = Gt ->
           P b1 (ocons a2 n2 b2) o ->
           P (ocons a1 n1 b1) (ocons a2 n2 b2)
             (ocons a1 n1 o)) ->
        (forall a1 n1 b1 a2 n2 b2 o,
           compare a1 a2 = Lt ->
           P (ocons a1 n1 b1) b2 o ->
           P (ocons a1 n1 b1) (ocons a2 n2 b2) 
           (ocons a2 n2 o)) ->
        (forall a1 n1 b1 a2 n2 b2 o,
           compare a1 a2 = Eq ->
           P b1 b2 o ->
          P (ocons a1 n1 b1) (ocons a2 n2 b2)
            (ocons a1 (S (n1 + n2)%nat) o)) ->
         forall a b, P a b (oplus a b).
Proof with auto.
   induction a.
   -    intro; simpl; destruct b;auto.
   -   induction b.
       + apply X0.
       + case_eq (compare a1 b1).
         * intro Comp; unfold oplus; rewrite Comp.
           cbn; apply X3 ...
         * intro Comp; cbn; rewrite Comp; apply X2...
         * intro Comp; cbn; rewrite Comp ...
 Defined.

Ltac oplus_induction a b:= pattern (oplus a b); apply oplus_rect.
\end{Coqsrc}

\begin{exercise}
The induction principle \texttt{oplus\_rect} is still unused in our development. 
Please build some nice examples of application.
\end{exercise}

>>>>

\textbf{Hint:}   Beware of the instances associated with sum and product of notations!
  You may consider additional fields 
to make the sum and product of notations ``compositional''.

@@

% \subsubsection{A hand-made induction principle}
% \label{sec:orgheadline85}

% \index{Coq!Commands!Functional Scheme}

% \emph{Coq} contains a command  \texttt{Functional Scheme} that 
% generates induction principles which correspond to recursive functions.
% Unfortunately, the current version ( \texttt{8.11.0} ) doesn't work on \texttt{oplus},
% probably because of the inner \texttt{Fix}.

% \begin{Coqsrc}
% Functional Scheme oplus_ind := Induction for oplus Sort Prop.
% \end{Coqsrc}

% \begin{Coqanswer}
% Error: Anomaly "todo." Please report at http://coq.inria.fr/bugs/.
% \end{Coqanswer}

% Fortunately, it's a good exercise for a semi-experienced user, to write
% her/him-self induction principles similar to the ones returned by
% \texttt{Functional Scheme}.

% \begin{itemize}
% \item First, we chose to write a version for sort \texttt{Type}, since versions
% for sorts \texttt{Prop} and \texttt{Set} can be easily derived from
% the former one. According to \emph{Coq}'s naming politics, we will call our 
% principle \texttt{oplus\_rect}

% \item The conclusion of \texttt{oplus\_rect} will be (\texttt{$P$ a b (oplus a b)}),
% where $P$ is an arbitrary function of type 
% \texttt{T1 -> T1 -> T1 -> Type}

% \item The premises of \texttt{oplus\_rect} will describe how to build an induction 
% on the graph of \texttt{oplus}.
% \end{itemize}

% We are now ready to state and prove \texttt{oplus\_rect}, and the reader
% will note that the statement is longer than the proof script itself,
% which is a standard proof by induction, simplification and case-analysis 
% that follows  \texttt{oplus}'s definition.

% We associate also a tactic to the application of \texttt{oplus\_rect}.

% \begin{Coqsrc}
%  Lemma oplus_rect:
%       forall P: T1 -> T1 -> T1 -> Type, 
%         (forall a:T1, P zero a a) ->
%         (forall a: T1, P a zero a) ->
%         (forall a1 n1 b1 a2 n2 b2 o,
%            compare a1 a2 = Gt ->
%            P b1 (ocons a2 n2 b2) o ->
%            P (ocons a1 n1 b1) (ocons a2 n2 b2)
%              (ocons a1 n1 o)) ->
%         (forall a1 n1 b1 a2 n2 b2 o,
%            compare a1 a2 = Lt ->
%            P (ocons a1 n1 b1) b2 o ->
%            P (ocons a1 n1 b1) (ocons a2 n2 b2) 
%            (ocons a2 n2 o)) ->
%         (forall a1 n1 b1 a2 n2 b2 o,
%            compare a1 a2 = Eq ->
%            P b1 b2 o ->
%           P (ocons a1 n1 b1) (ocons a2 n2 b2)
%             (ocons a1 (S (n1 + n2)%nat) o)) ->
%          forall a b, P a b (oplus a b).
% Proof with auto.
%    induction a.
%    -    intro; simpl; destruct b;auto.
%    -   induction b.
%        + apply X0.
%        + case_eq (compare a1 b1).
%          * intro Comp; unfold oplus; rewrite Comp.
%            cbn; apply X3 ...
%          * intro Comp; cbn; rewrite Comp; apply X2...
%          * intro Comp; cbn; rewrite Comp ...
%  Defined.

% Ltac oplus_induction a b:= pattern (oplus a b); apply oplus_rect.
% \end{Coqsrc}

% \index{Exercises}

% \begin{exercise}
% The induction principle \texttt{oplus\_rect} is still unused in our development. 
% Please build some nice examples of application.
% \end{exercise}
